Validating the perioperative thirst discomfort scale for measuring thirst discomfort prior to procedures

### 2020-08-17 manuscript/index.Rmd
plan with word manuscript

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.retina = 5)
# tint options
library(tint)
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tint'))
options(htmltools.dir.version = FALSE)
library(drake)
library(magrittr)
library(flextable)

@@

```{r tab.cap="Participant characteristics", tab.id = 'tab1'}
drake::loadd(summary_table)
# gtsummary::as_flextable(summary_table)
gtsummary::as_kable_extra(summary_table, booktabs = T)
```

@@

```{r tab.id = "tab2", tab.cap= "Item hierarchy of the PTDS-5"}
# flextable::flextable(drake::readd(item_hierarchy_df_ptds5)) %>% 
#   autofit()
drake::readd(item_hierarchy_df_ptds5) %>% 
  kableExtra::kable(booktabs = T)
```

@@

```{r tab.id='Hvaluesptds7', tab.cap.pre="Appendix Table ", tab.cap = "Homogeneity values (and standard errors) for all items in the PTDS"}
drake::readd(H_values_ptds7_table) %>% 
  # flextable::flextable() %>% 
  # autofit()
  kableExtra::kable(booktabs = T)
```

@@

# flextable::flextable(drake::readd(monotonicity_df_ptds6_table)) %>%  
#   autofit()
 drake::readd(monotonicity_df_ptds6_table) %>% 
kableExtra::kable(booktabs = T)
```

@@

```{r tab.id='aisp', tab.cap.pre="Appendix Table ", tab.cap = "aisp for increasing H thresholds (*c*)"}
# flextable::flextable(drake::readd(aisp)) %>% 
  # autofit()
drake::readd(aisp) %>% 
  kableExtra::kable(booktabs = T)
```

@@

```{r tab.id='iioptds6', tab.cap.pre="Appendix Table ", tab.cap = "Invariant item ordering for PTDS-6"}
drake::readd(iio_ptds6_table) %>% 
  # flextable() %>% 
  # autofit()
  kableExtra::kable(booktabs = T)
```

@@

```{r tab.id='iioptds5', tab.cap.pre="Appendix Table ", tab.cap = "Invariant item ordering for PTDS-5"}
drake::readd(iio_ptds5_table) %>%
    # flextable() %>%
    # autofit()
  kableExtra::kable(booktabs = T)
```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.retina = 5)
options(htmltools.dir.version = FALSE)
library(drake)
library(magrittr)
library(flextable)

@@

```{r tab.cap="Participant characteristics", tab.id = 'tab1'}
drake::loadd(summary_table)
gtsummary::as_flextable(summary_table)
# gtsummary::as_kable_extra(summary_table, booktabs = T)
```

@@

```{r tab.id = "tab2", tab.cap= "Item hierarchy of the PTDS-5"}
flextable::flextable(drake::readd(item_hierarchy_df_ptds5)) %>%
  autofit()
# drake::readd(item_hierarchy_df_ptds5) %>% 
#   kableExtra::kable(booktabs = T)
```

@@

```{r tab.id='Hvaluesptds7', tab.cap.pre="Appendix Table ", tab.cap = "Homogeneity values (and standard errors) for all items in the PTDS"}
drake::readd(H_values_ptds7_table) %>% 
  flextable::flextable() %>%
  autofit()
  # kableExtra::kable(booktabs = T)
```

@@

flextable::flextable(drake::readd(monotonicity_df_ptds6_table)) %>%
  autofit()
#  drake::readd(monotonicity_df_ptds6_table) %>% 
# kableExtra::kable(booktabs = T)
```

@@

```{r tab.id='aisp', tab.cap.pre="Appendix Table ", tab.cap = "aisp for increasing H thresholds (*c*)"}
flextable::flextable(drake::readd(aisp)) %>%
autofit()
# drake::readd(aisp) %>% 
#   kableExtra::kable(booktabs = T)
```

@@

```{r tab.id='iioptds6', tab.cap.pre="Appendix Table ", tab.cap = "Invariant item ordering for PTDS-6"}
drake::readd(iio_ptds6_table) %>% 
  flextable() %>%
  autofit()
  # kableExtra::kable(booktabs = T)
```

@@

```{r tab.id='iioptds5', tab.cap.pre="Appendix Table ", tab.cap = "Invariant item ordering for PTDS-5"}
drake::readd(iio_ptds5_table) %>%
    flextable() %>%
    autofit()
  # kableExtra::kable(booktabs = T)
```
